\section{Silicon Showcase}
\label{sec:silicon_showcase}

A curated list showcasing the types of designs possible through Tiny Tapeout is provided below:

\begin{itemize}
    \item Serial FPGA~\cite{showcaseserialfpga}: a one fracturable 5-LUT that receives FPGA LUT configuration frames and serially evaluates LUT inputs and LUT outputs.
    \item Synthesizable digital temperature sensor~\cite{showcasetempsense}: a design which creatively twists the use of a tristate-inverter (EINVP) to create voltage  digital to analog converter (DAC). This voltage-mode DAC is used to bias an NMOS into subthreshold operation to discharge the input capacitor of an inverter. Since the subthreshold current of a MOSFET is a strong function of temperature, the resulting delay time is also a strong function of temperature, thus a digital temperature sensor is created.
    \item 395 standard cells with multiplexer~\cite{showcasemicrotapeout}: a design which contains a copy of most standard cells in the SkyWater sky130\_fd\_sc\_hd library along with a multiplexing mechanism that allows the user to expose any of them to the input/output pins.
    \item FM transmitter with I2S input~\cite{showcasefmtx}: a design which takes an audio signal and modulates it to a higher carrier frequency using frequency modulation (FM). The modulator in this design is based on a numerically controlled oscillator (NCO) with several modifications.
    \item USB Full Speed device~\cite{showcaseusb}: a hardware implementation of a USB Device hardware interface, designed to be compliant with USB1.1 Full Speed/Low Speed modes but not High Speed.
    \item A Linux capable RISC-V CPU~\cite{showcasekianv}: a functional RV32IMA RISC-V processor designed to boot and run the uLinux Linux distribution for resource constrained devices.
\end{itemize}

An index of all designs submitted to Tiny Tapeout can be found at \url{TinyTapeout.com/runs/}~\cite{tinytapeoutruns}.
